A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2020-12-25 paper.tex
Harold's edits to abstract

    The small (1 mm) nematode \emph{Caenorhabditis elegans} has become widely used as a model organism; in particular the \emph{C. elegans} connectome has been completely mapped, and \emph{C. elegans} locomotion has been widely studied (c.f. http://www.wormbook.org \citet{corsi2015}). We describe a minimal reaction-diffusion model for the \emph{C. elegans}, which results in similar behaviour to the neuromechanical model of \citet{izquierdo2018}. This  may be considered as a simple model for Xu et al.'s "descending pathway" description of the \emph{C. elegans} central pattern generator (CPG) \citet{xu2018,wen2012}. \citet{olivares2019} present a likely more realistic model which relies on small networks of neurons, and presents a distributed model of the CPG. In particular, we use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C. elegans} undulation (see \citet{magnes2012}), and thus locomotion.  Finally, we recreate the required oscillations and coupling with a network of coupled \citet{keener1983} analog neurons.
    \citet{olivares2019}
    % TODO: expand and inflate; fix grammar, cite Olivares2019, \citet @article{olivares2018potential}

\end{abstract}

@@

\begin{figure}[h!]
    \centering
    \inputtikz{figures/cpg/cpg}
    \label{fig: cpg}
    \caption{Our simplified central pattern generator model.  Descending coupling (shows inhibitory connections, and potential flows through gap junctions, not necessarily symmetric)}
\end{figure} % TODO: legend

@@

\begin{figure}[h!]
    \label{fig: fhn_dynamics}
    \centering
    \includegraphics{figures/fhn_dynamics/fhn_dynamics.pdf}
    \caption{The nullclines of the FitzHugh-Nagumo neuron.  Nullclines are isoclines where the derivative of a variable is zero.  Here we show an oscillatory mode and an excitable one.  In an oscillating cell, the stable equilibrium is replaced by an unstable equilibrium (open circle) around which it circles indefinitely.  See \citet{parsons2018} for a clear explanation of the dynamics of oscillatory biological systems.}
\end{figure} % TODO: legend

>>>>

    The small (1 mm) nematode \emph{Caenorhabditis elegans} \cite{corsi2015} has become widely used as a model organism; in particular the \emph{C. elegans} connectome has been completely mapped, and \emph{C. elegans} locomotion has been widely studied (\citet{corsi2015}). We describe a minimal reaction-diffusion model for the locomotion of \emph{C. elegans}, using as a framework a simplified version of Xu et al.'s "descending pathway" description of the \emph{C. elegans} central pattern generator (CPG) \citet{xu2018,wen2012}.  Finally, we realize a model of the required oscillations and coupling with a network of coupled \citet{keener1983} analog neurons.
    We note that \citet{olivares2019} present a likely more realistic model which relies on small networks of neurons, and presents a distributed model of the CPG. In particular, we use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C. elegans} undulation (see \citet{magnes2012}), and thus locomotion.
\end{abstract}

@@

\begin{figure}[h!]
    \ContinuedFloat
    \centering
    \inputtikz{figures/cpg/cpg}
    \label{fig: cpg}
    \caption{Our simplified central pattern generator model.  Descending coupling (shows inhibitory connections, and potential flows through gap junctions, not necessarily symmetric)}
\end{figure} % TODO: legend

@@

\begin{figure}[h!]
    \label{fig: fhn_dynamics}
    \centering
    \includegraphics[height=5cm]{figures/fhn_dynamics/fhn_dynamics.pdf}
    \caption{The nullclines of the FitzHugh-Nagumo neuron.  Nullclines are isoclines where the derivative of a variable is zero.  Here we show an oscillatory mode and an excitable one.  In an oscillating cell, the stable equilibrium is replaced by an unstable equilibrium (open circle) around which it circles indefinitely.  See \citet{parsons2018} for a clear explanation of the dynamics of oscillatory biological systems.}
\end{figure} % TODO: legend
